\documentclass[a4paper,10pt]{article}

\usepackage[a4paper,margin=0.7in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}
\usepackage{parskip}

\setlength{\parindent}{0pt}
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]

\begin{document}

\begin{center}
    {\LARGE \textbf{SHILPA}}\\[5pt]
    {{role}}\\
    \href{mailto:gopidishilpa11@gmail.com}{gopidishilpa11@gmail.com} \;|\;
    +1 (614)-683-9466
\end{center}

%--------------------------------------------------------

\section*{Professional Summary}

\begin{itemize}[leftmargin=*]
\item {{summary_s1}}
\item {{summary_s2}}
\item {{summary_s3}}
\item {{summary_s4}}
\item {{summary_s5}}
\end{itemize}

%--------------------------------------------------------

\section*{Technical Skills}

\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     {{skills_healthcare}} \\
     {{skills_ba}} \\
     {{skills_tools}} \\
     {{skills_databases}} \\
     {{skills_technologies}} \\
     {{skills_methodologies}}
    }}
\end{itemize}

%--------------------------------------------------------

\section*{Professional Experience}

\textbf{Sr. Business Analyst -- Healthcare}\\
State of NY (DHHS), NY, USA \hfill June 2024 -- Present

\begin{itemize}[leftmargin=*]
\item {{project1_bullet1}}
\item {{project1_bullet2}}
\item {{project1_bullet3}}
\item {{project1_bullet4}}
\item Collaborate with development teams on functional specifications.
\item Perform data mapping and system integration.
\item Ensure HIPAA, SOX, and PCI compliance.
\item Support UAT, defect tracking, and business validation.
\item Coordinate offshore teams.
\item Develop dashboards and KPI reports.
\item Participate in Agile ceremonies.
\item Coordinate QA, test plans, and UAT.
\item Analyze healthcare data using SQL and Excel.
\item Identify automation opportunities.
\item Support REST/SOAP API integrations.
\item Facilitate stakeholder communication.
\item Monitor project progress.
\item Assist change management.
\item Improve business processes.
\end{itemize}

\vspace{4mm}

\textbf{Sr. Business Analyst -- Healthcare}\\
CVS Health, Woonsocket, RI, USA \hfill Apr 2021 -- Jan 2024

\begin{itemize}[leftmargin=*]
\item {{project2_bullet1}}
\item {{project2_bullet2}}
\item {{project2_bullet3}}
\item {{project2_bullet4}}
\item Supported OCR-based claims automation.
\item Created test plans and UAT documentation.
\item Gathered business requirements.
\item Performed SQL and Excel data analysis.
\item Developed workflow diagrams using Visio.
\item Supported defect resolution.
\item Ensured HIPAA compliance.
\item Collaborated with QA and Development teams.
\item Mentored junior analysts.
\end{itemize}

\vspace{4mm}

\textbf{Business Analyst / Process Analyst}\\
Cigna, India \hfill Nov 2017 -- Mar 2021

\begin{itemize}[leftmargin=*]
\item Worked on claims, eligibility, and billing systems.
\item Conducted requirement gathering.
\item Created process maps and functional specifications.
\item Supported automation initiatives.
\item Ensured HIPAA compliance.
\item Coordinated with cross-functional teams.
\end{itemize}

\vspace{4mm}

\textbf{Junior Business Analyst / Developer}\\
Accenture, India \hfill Aug 2015 -- Nov 2017

\begin{itemize}[leftmargin=*]
\item Assisted in requirement gathering.
\item Created user stories and workflow documentation.
\item Supported development and testing teams.
\item Participated in Agile ceremonies.
\end{itemize}

%--------------------------------------------------------

\section*{Education}

\textbf{Bachelor's Degree in Computer Science}\\
Sri Indu Institute of Engineering and Technology (JNTUH)\\
Graduated: 2015

\end{document}
