\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\setlist[itemize]{noitemsep, topsep=1pt, parsep=0.5pt, partopsep=0pt}
\usepackage[colorlinks=true, linkcolor=black, urlcolor=blue]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins to fit on 2 pages cleanly
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}
\setlength{\footskip}{4.0pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

% Ensure generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{#1}\vspace{-2pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADER----------
\begin{center}
    {\Huge \scshape YESHWANTH YELLANKI} \\ \vspace{2pt}
    \small Wichita, KS ~|~ (316) 932-4488 ~|~ 
    \href{mailto:yellanki.yeshwanth@gmail.com}{yellanki.yeshwanth@gmail.com} ~|~ 
    \href{http://www.linkedin.com/in/yesh284}{linkedin.com/in/yesh284}
\end{center}

%-----------PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
\resumeItemListStart
    \resumeItem{{{summary_s1}}}
    \resumeItem{{{summary_s2}}}
    \resumeItem{{{summary_s3}}}
    \resumeItem{Designed and optimized data processing pipelines, backend integrations, and event driven workflows supporting analytics, reporting, and operational reliability initiatives.}
    \resumeItem{Experienced collaborating with platform engineering, security, QA, and business stakeholders to deliver reliable systems under production constraints and evolving business requirements.}
\resumeItemListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     {{skills_programming}} \\
     {{skills_frameworks}} \\
     {{skills_cloudops}} \\
     {{skills_architecture}} \\
     {{skills_tools}} \\
     {{skills_ai}}
    }}
\end{itemize}

%-----------PROFESSIONAL EXPERIENCE-----------
\section{Professional Experience}
\resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer}{Dec 2025 -- Feb 2026}
      {TVR Consulting LLC}{Remote, US}
      \resumeItemListStart
        \resumeItem{Engineered cloud native ETL workflows using Python and AWS services to process and normalize operational datasets supporting downstream analytics and reporting across multiple business functions.}
        \resumeItem{Automated ingestion and transformation pipelines handling 200K+ records per execution cycle, reducing manual reconciliation effort by 45\% while improving reporting consistency.}
        \resumeItem{Optimized relational database queries and indexing strategies across PostgreSQL environments, improving query response times by 35\% under concurrent reporting workloads.}
        \resumeItem{Implemented monitoring and validation checkpoints within data pipelines to detect schema drift, failed transformations, and incomplete loads before downstream propagation.}
        \resumeItem{Partnered with analysts and business stakeholders to translate ambiguous reporting requirements into production ready data models and reusable transformation logic.}
        \resumeItem{Strengthened deployment reliability through standardized environment configuration, logging, and operational runbooks that reduced troubleshooting time during production incidents.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer}{Oct 2024 -- Nov 2025}
      {Experian}{Remote, US}
      \resumeItemListStart
        \resumeItem{{{project1_bullet1}}}
        \resumeItem{{{project1_bullet2}}}
        \resumeItem{{{project1_bullet3}}}
        \resumeItem{{{project1_bullet4}}}
        \resumeItem{Orchestrated automated vulnerability remediation for 30+ Amazon Linux EC2 instances using AWS Systems Manager, patch baselines, and maintenance windows, eliminating configuration drift and reducing manual maintenance cycles.}
        \resumeItem{Integrated Veracode and SonarQube quality gates into Jenkins CI/CD pipelines, improving code maintainability metrics and reducing critical code quality violations prior to production deployment.}
        \resumeItem{Contributed to migration of legacy workloads into containerized Docker and Kubernetes environments, improving deployment consistency and enabling scalable microservices delivery across shared infrastructure platforms.}
        \resumeItem{Built serverless workflow orchestration pipelines using AWS Step Functions and Lambda to support stateful event processing and operational automation across distributed systems.}
        \resumeItem{Designed AWS infrastructure architecture diagrams documenting EC2 hosted Kafka integrations, downstream analytics flows, and cross account communication patterns used by engineering and platform teams.}
        \resumeItem{Led production deployment activities including change request approvals, release coordination, rollback validation, and post deployment issue resolution for business critical application updates.}
        \resumeItem{Authored operational documentation, deployment procedures, and troubleshooting guides that improved onboarding efficiency and reduced dependency on tribal knowledge across engineering teams.}
        \resumeItem{Collaborated with security, platform engineering, QA, and business stakeholders throughout the SDLC to improve release quality, deployment governance, and production stability.}
      \resumeItemListEnd

    \resumeSubheading
      {Database Specialist}{Jul 2023 -- Oct 2023}
      {Ticket Socket Inc}{Remote, US}
      \resumeItemListStart
        \resumeItem{Managed large scale Excel based operational datasets supporting venue allocation and seating logistics for FIBA World Cup event preparation across multiple venues and stakeholder groups.}
        \resumeItem{Validated and reconciled structured event data to improve downstream reporting accuracy and reduce inconsistencies impacting logistics coordination and operational planning.}
        \resumeItem{Automated repetitive data validation workflows and spreadsheet reconciliation tasks, reducing manual processing effort and improving turnaround time for operational reporting requests.}
        \resumeItem{Coordinated with event operations teams to resolve data discrepancies under tight delivery timelines while maintaining data integrity across rapidly changing scheduling requirements.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer}{Nov 2021 -- Aug 2022}
      {Cognizant Technology Solutions}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{{{project2_bullet1}}}
        \resumeItem{{{project2_bullet2}}}
        \resumeItem{{{project2_bullet3}}}
        \resumeItem{{{project2_bullet4}}}
        \resumeItem{Implemented automated unit and integration testing frameworks using Jest and Cypress, increasing frontend test coverage by 30\% and improving release confidence across development cycles.}
        \resumeItem{Participated in Agile delivery processes including sprint planning, code reviews, defect resolution, and collaborative debugging to improve delivery quality and reduce regression issues.}
        \resumeItem{Contributed to reusable UI component development and API integration efforts that accelerated feature delivery timelines across multiple project modules.}
      \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------TECHNICAL PROJECTS-----------
\section{Technical Projects}
\resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{AI Powered Resume Builder} $|$ \emph{React, Tailwind CSS, OpenAI, Node.js, ATS Scoring, Strapi, Vite}}{2025}
      \resumeItemListStart
        \resumeItem{Architected and developed a full-stack AI powered resume platform enabling dynamic resume generation, ATS scoring, and content optimization using OpenAI APIs and Node.js backend services.}
        \resumeItem{Built responsive frontend workflows using React and Tailwind CSS, enabling users to create, edit, and export resumes through optimized multi step interfaces.}
        \resumeItem{Integrated AI driven recommendation workflows to generate contextual resume suggestions and improve keyword alignment for ATS compatibility.}
        \resumeItem{Implemented authentication and session management using Clerk while securing API interactions and user specific document operations.}
        \resumeItem{Designed reusable REST API integrations and modular frontend components to support maintainability and future feature scalability.}
        \resumeItem{Deployed production ready application architecture using Vite and modern frontend build optimization techniques.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Diabetic Retinopathy Classification} $|$ \emph{Deep Learning, CNN, Binary Classification}}{2022}
      \resumeItemListStart
        \resumeItem{Developed a CNN based image classification model for diabetic retinopathy detection using large scale retinal image datasets and supervised deep learning techniques.}
        \resumeItem{Improved model accuracy from 92\% to 98\% through iterative hyperparameter tuning, architecture refinement, and overfitting reduction strategies.}
        \resumeItem{Applied preprocessing, validation, and training optimization techniques to improve model generalization across unseen clinical image samples.}
        \resumeItem{Evaluated model performance using classification metrics and validation datasets to ensure prediction reliability and consistency.}
      \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------CERTIFICATIONS AND PUBLICATIONS-----------
\section{Certifications and Research Publications}
\resumeItemListStart
    \resumeItem{\textbf{AWS Certified Cloud Practitioner} $|$ View Certification (Mar 2026)}
    \resumeItem{\textbf{E Challan System for Non-Parking Areas} $|$ View Publication (Apr 2021)}
\resumeItemListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Wichita State University}{Wichita, KS}
    {Master of Science in Data Science}{May 2024}
  \resumeSubheading
    {SCSVMV University}{Tamil Nadu, India}
    {Bachelor of Engineering in Computer Science and Engineering}{May 2021}
\resumeSubHeadingListEnd

\end{document}
